TSELM: Target speaker extraction using discrete tokens and language models

### 2024-09-06 src/paper.tex
update

\subsection{Baseline models}
Baseline models are presented in Table \ref{main_exp}. 
TSELM is compared with Spex+ \cite{spex_plus}, a discriminative separation model trained on Libri2Mix \cite{librimix}. Since discretization can potentially lose speaker information compared to continuous methods. We compute the speaker 
similarity of output from TSELM with the target audio produced by discretizing the clean audio, denoted by Target-Discrete, representing the upper bound of our model  
performance. Besides TSELM, we conduct three main experiments 
denoted by Continuous-WavLM-L6, TSELM-L-Hybrid and TSELM-S-NoConcat using the same training data. 
For Continuous-WavLM-6, we directly
passed the embeddings of the 6th hidden layer output of WavLM to the cross attention  
and LM. Concatenation strategy is stilled applied to the mixed speech. Mean Square Error (MSE) loss is applied between the output embeddings and the clean 
embeddings. HiFi-GAN in \cite{knn_vc} is used to reconstruct the audio. For 
TSELM-L-Hybrid, inspired by MaskSR \cite{mask_sr}, we kept discretizing the reference 
speech while utilizing the continuous embeddings from the reference speech. We call 
it hybrid instead of fully discretized because the mixture speech has continuous 
features instead of discrete features. For TSELM-S-NoConcat, we utilize the TSELM-S model architecture but without concatenation strategy.

>>>>

\subsection{Baseline models}
Baseline models are presented in Table \ref{main_exp}. 
TSELM is compared with Spex+ \cite{spex_plus}, a discriminative separation model trained on Libri2Mix \cite{librimix}. Since discretization can potentially lose speaker information compared to continuous methods. We compute the speaker 
similarity of output from TSELM with the target audio produced by discretizing the clean audio, denoted by Target-Discrete, representing the upper bound of our model  
performance. Besides TSELM, we conduct three main experiments, named
 Continuous-WavLM-L6, TSELM-L-Hybrid and TSELM-S-NoConcat using the same training data. 
For Continuous-WavLM-6, we directly
pass the embeddings from the 6th hidden layer output of WavLM Large to the cross attention  
and LM without discretization. 
The concatenation strategy is stilled applied to the mixed speech. Mean Square Error (MSE) loss is applied between the output embeddings and the clean 
embeddings. HiFi-GAN in \cite{knn_vc} is used for audio reconstruction. For 
TSELM-L-Hybrid, inspired by MaskSR \cite{mask_sr}, we discretize the reference 
speech while utilizing the continuous embeddings from the mixed speech. We call 
it hybrid because the mixture speech retains continuous features. In TSELM-S-NoConcat, we utilize the TSELM-S model architecture but without concatenation strategy.
